---
title: "week35"
author: "Tristan Caro"
date: "8/24/2021"
output: html_document
---

# Get the Data

Read in with tidytuesdayR package 
Install from CRAN via: `install.packages("tidytuesdayR")`
This loads the readme and all the datasets for the week of interest

Either ISO-8601 date or year/week works!

Or read in the data manually:

```
lemurs <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-08-24/lemur_data.csv')
```


```{r}
library(tidyverse)
library(tidytuesdayR)
library(ggtext)
library(ggdist)

lemurs <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-08-24/lemur_data.csv')

theme_set(theme_minimal(base_size = 10))
```

# Latest recorded weight by specimen ID
Source: https://twitter.com/leeolney3/status/1430085673025949696/photo/1
@leeolney
```{r}
weight <- lemurs %>%
  mutate(age_cat = case_when(age_category == "young_adult" ~ "Young-Adult",
                             age_category == "IJ" ~ "Infant/Juvenile",
                             age_category == "adult" ~ "Adult"),
         gender = case_when(sex == "F" ~ "Female",
                            sex == "M" ~ "Male")
  ) %>% 
  mutate(group = paste(age_cat, gender)) %>% 
  mutate(group = factor(group, levels = c("Adult Female", 
                                          "Adult Male", 
                                          "Young-Adult Female", 
                                          "Young-Adult Male",
                                          "Infant/Juvenile Female",
                                          "Infant/Juvenile Male",
                                          "Infant/Juvenile NA"),
                        ordered = TRUE)) %>% 
  group_by(dlc_id) %>% 
  slice(which.max(weight_date))

```

# Box plot with bar code strips
Source: https://twitter.com/leeolney3/status/1430085673025949696/photo/1
@leeolney
```{r}
p_weight = weight %>% 
  ggplot(aes(y = weight_g, x = group, color = group)) +
  geom_boxplot(
    width = 0.2,
    outlier.shape = NA,
    fill = "#f4f4f2",
    position = position_nudge(x = 0.2, y = 0)) +
  geom_point(
    shape = 95,
    size = 6,
    alpha = 0.2,
    position = position_nudge(x = -0.1, y = 0)) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15)) +
  scale_color_manual(values = c("#003049", "#003049",
                                "#f77f00", "#003049",
                                "#003049", "#003049",
                                "#003049")) +
  theme(
    legend.position = "none",
    panel.grid = element_line(size = 0.2, color = "#ced4da"),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    axis.title.x = element_markdown(size = 8.2, margin=margin(t=8)),
    axis.title.y = element_markdown(size= 8.2, margin=margin(r=8)),
    axis.text.x=element_text(size=7.5, margin = margin(t=-5)),
    plot.caption = element_text(size = 7.5, color="#495057"),
    plot.title.position = "plot",
    plot.title = element_text(face = "bold", size = 13),
    plot.subtitle = element_text(size = 8),
    plot.margin = unit(c(.5, .5, .5, .5), "cm"),
    plot.background = element_rect(fill = "#f4f4f2", color = NA)) +
  labs(x = "**Age and gender group**",
       y = "**Latest weight recorded** (grams)",
       caption = "#TidyTuesday Week 35 | Data from Duke Lemur Center",
       title = "Weight of lemurs",
       subtitle = "by age category and gender (latest date by specimen ID), wehre Young Adult Females have the highest median weight at 2155 grams.")
```

# Raincloud plot
```{r}
color_scale <-  c("#003049", "#003049",
                  "#f77f00", "#003049",
                   "#003049", "#003049",
                   "#003049")

p_weight_cloud = weight %>% 
  ggplot(aes(y = weight_g, x = group, color = group, fill = group)) +
  geom_dotsinterval(size = 2) +
  stat_halfeye(
    position = position_nudge(x = -0.1, y = 0)) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15)) +
  scale_color_manual(values = color_scale) +
  scale_fill_manual(values = color_scale) +
  theme(
    legend.position = "none",
    panel.grid = element_line(size = 0.2, color = "#ced4da"),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    axis.title.x = element_markdown(size = 8.2, margin=margin(t=8)),
    axis.title.y = element_markdown(size= 8.2, margin=margin(r=8)),
    axis.text.x=element_text(size=7.5, margin = margin(t=-5)),
    plot.caption = element_text(size = 7.5, color="#495057"),
    plot.title.position = "plot",
    plot.title = element_text(face = "bold", size = 13),
    plot.subtitle = element_text(size = 8),
    plot.margin = unit(c(.5, .5, .5, .5), "cm"),
    plot.background = element_rect(fill = "#f4f4f2", color = NA)) +
  labs(x = "**Age and gender group**",
       y = "**Latest weight recorded** (grams)",
       caption = "#TidyTuesday Week 35 | Data from Duke Lemur Center",
       title = "Weight of lemurs",
       subtitle = "by age category and gender (latest date by specimen ID), wehre Young Adult Females have the highest median weight at 2155 grams.")
p_weight_cloud
```

# Weight pregnant versus not pregnant
Look into differences in weight based on pregnancy status. Filtering out male lemurs and juveniles.
```{r}
weight_preg <- weight %>% 
  filter(group == "Adult Female")
```

```{r}
color_scale_2 <-  c("#003049", "#f77f00")

p_weight_preg <- weight_preg %>% 
  ggplot(aes(y = weight_g, x = preg_status)) +
    geom_dotsinterval(
      size = 2,
      binwidth = 50) +
    stat_halfeye(
      scale = 0.3,
      side = "left") +
    scale_x_discrete(labels = function(x) str_wrap(x, width = 15)) +
    #scale_fill_manual(values = color_scale_2) +
    #scale_color_manual(values = color_scale_2) +
    theme(
      legend.position = "none",
      panel.grid = element_line(size = 0.2, color = "#ced4da"),
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_blank(),
      axis.title.x = element_markdown(size = 8.2, margin=margin(t=8)),
      axis.title.y = element_markdown(size= 8.2, margin=margin(r=8)),
      axis.text.x=element_text(size=7.5, margin = margin(t=-5)),
      plot.caption = element_text(size = 7.5, color="#495057"),
      plot.title.position = "plot",
      plot.title = element_text(face = "bold", size = 13),
      plot.subtitle = element_text(size = 8),
      plot.margin = unit(c(.5, .5, .5, .5), "cm"),
      plot.background = element_rect(fill = "#f4f4f2", color = NA)) +
    labs(x = "**Pregnancy Status**",
         y = "**Latest weight recorded** (grams)",
         caption = "#TidyTuesday Week 35 | Data from Duke Lemur Center",
         title = "Weight of lemurs",
         subtitle = "by pregnancy status.")
p_weight_preg
```



